Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-03 sections/background.tex
edited introduction and background sections

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}.
The grey area shows the review process of the system which composed of four main steps:
(1) an author creates a patch and submits a set of new or modified files as a review request to Gerrit system.
(2) reviewers examine the proposed code changes for defects or concerns.
(3) reviewers provide comments to the author.
The author creates a revised proposed change according to the comments and re-submits for review.
Then, reviewers will examine the revised proposed change.
If the revision is not approved, reviewers provide comments to fix and the process continues until
(4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (rejected).

According to this process, reviewers' comments are the most important factor in determining software quality.
In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness.
% (e.g. coding styles, documentation, process workflow, etc.)
For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design issues \cite{Bacchelli2013a}.
Our observations of the Qt project also correspond to this finding.
We found that some comments are superficial and unhelpful to the proposed changes.
For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information,
while the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

>>>>

An overview of MCR process based on the Gerrit code review system is shown in Fig. \ref{fig:process}.
The grey area shows the review process of the system which is composed of four main steps:
(1) An author creates a patch and submits a set of new or modified files as a review request to the Gerrit system.
(2) Reviewers examine the proposed code changes for defects or concerns.
(3) Reviewers provide comments to the author.
The author creates a revised proposed change according to the comments and re-submits for review.
Reviewers then examine the revised proposed change.
If the revision is not approved, reviewers provide comments to fix and the process continues until
(4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (rejected).

According to this process, reviewers' comments are the most important factor in determining software quality.
In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion (i.e. no comments) are likely to contain bugs.
However, it has not been shown that components with comments are less likely to contain bugs. Tools supporting MCR such as Gerrit allow reviewers to freely write messages to authors (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness and consequently may have little impact on quality.
% (e.g. coding styles, documentation, process workflow, etc.)
For example, a comment may be related to something outside the scope of the proposed change, perhaps author or reviewer personal issues or inter-personal communication e.g. ``Keep up the good work everyone!".
Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design issues \cite{Bacchelli2013a}.
Our observations of the Qt project also corroborate this finding.
We found that many examples of comments that are superficial and unhelpful to the proposed changes.
For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is certainly within the scope of the proposed change, yet provides little useful information.
While the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope, and not directly useful for the proposed change.

Ultimately our aim is to understand the impact of useful and useless comments on code quality. Specifically, what degree of useful comments are needed to effect positive impact on quality. Study of this necessitates ascertaining, with high confidence, the usefulness of a large number of comments. This  had proven difficult to accomplish manually, so here we investigate the pragmatics of using semantic similarity to assist with this task.

### 2014-08-03 sections/introduction.tex
edited introduction and background sections

Prior research has focused primarily on the relationship between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, an effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
So while the data may be easy to access, MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
Moreover, given that comments in MCR are unstructured natural text, open to subjective judgment, contain tacit understanding, and possible misinterpretation, assessment errors are inevitable.

@@

In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
As manual classification can quickly become an untenable task, our proposed approach is meant to ease classifying large amounts of MCR comments in order to conduct comment and code quality studies (such as those discussed earlier).
By introducing automation support for assessment grounded with objective empirical criteria, our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MCR data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Hence through our case study of Qt project, in this work we explore the following research questions:
\begin{ResearchQuestions}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{ResearchQuestions}

Our contributions are as follows:
\begin{itemize}
\item An investigation on the practicality of mining natural text comments in code reviews to classify their usefulness using semantic similarity.
\item Determination and validation of a model relating usefulness of comments and semantic similarity.
\item A case-study application and performance analysis of the model for a large open source project based (Qt) on actual human effort.
\end{itemize}

>>>>

Prior research has focused primarily on the relationship between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, an effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
So while the data may be easy to access, MCR can produce a massive amounts of change requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
Moreover, given that comments in MCR are unstructured natural text, open to subjective judgment, contain tacit understanding, and possible misinterpretation, assessment errors are inevitable.

@@

In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
As manual classification can quickly become an untenable task, our proposed approach is meant to ease classifying large amounts of MCR comments in order to conduct comment and code quality studies (such as those discussed earlier).
By introducing automation support for assessment grounded with objective empirical criteria, our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MCR data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Hence through our case study of Qt project, in this work we explore the following research questions:
\begin{ResearchQuestions}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable for large MCR data sets?
\end{ResearchQuestions}

The contributions in this paper are as follows:
\begin{itemize}
\item An investigation on the practicality of mining natural text comments in code reviews to classify their usefulness using semantic similarity.
\item Determination and validation of a model relating usefulness of comments and semantic similarity.
\item A case-study application and performance analysis of the model for a large open source project based (Qt) on actual human effort.
\end{itemize}
